### 2019-05-08 manuscript/journal-applied-entomology/main.tex
updated title

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A template for Wiley article submissions.
% Developed by Overleaf. 
%
% Please note that whilst this template provides a 
% preview of the typeset manuscript for submission, it 
% will not necessarily be the final publication layout.
%
% Usage notes:
% The "blind" option will make anonymous all author, affiliation, correspondence and funding information.
% Use "num-refs" option for numerical citation and references style.
% Use "alpha-refs" option for author-year citation and references style.

\documentclass[alpha-refs]{wiley-article}
% \documentclass[blind,num-refs]{wiley-article}

% Add additional packages here if required
\usepackage{siunitx}

% Update article type if known
\papertype{Original Article}
% Include section in journal if known, otherwise delete
\paperfield{Journal Section}

\title{Camila Title Suggestions?}

% List abbreviations here, if any. Please note that it is preferred that abbreviations be defined at the first instance they appear in the text, rather than creating an abbreviations list.
\abbrevs{ABC, a black cat; DEF, doesn't ever fret; GHI, goes home immediately.}

% Include full author names and degrees, when required by the journal.
% Use the \authfn to add symbols for additional footnotes and present addresses, if any. Usually start with 1 for notes about author contributions; then continuing with 2 etc if any author has a different present address.
\author[1\authfn{1}]{Author One PhD}
\author[2\authfn{1}]{Author A.~Two MD}
\author[2\authfn{2}]{Author Three PhD}
\author[2]{Author B.~Four}

\contrib[\authfn{1}]{Equally contributing authors.}

% Include full affiliation details for all authors
\affil[1]{Department, Institution, City, State or Province, Postal Code, Country}
\affil[2]{Department, Institution, City, State or Province, Postal Code, Country}

\corraddress{Author One PhD, Department, Institution, City, State or Province, Postal Code, Country}
\corremail{correspondingauthor@email.com}

\presentadd[\authfn{2}]{Department, Institution, City, State or Province, Postal Code, Country}

\fundinginfo{Funder One, Funder One Department, Grant/Award Number: 123456, 123457 and 123458; Funder Two, Funder Two Department, Grant/Award Number: 123459}

% Include the name of the author that should appear in the running header
\runningauthor{Author One et al.}

\begin{document}

\maketitle

\begin{abstract}
This is a generic template designed for use by multiple journals, which includes several options for customization. Please consult the author guidelines for the journal to which you are submitting in order to confirm that your manuscript will comply with the journal's requirements. Please replace this text with your abstract.

% Please include a maximum of seven keywords
\keywords{keyword 1, \emph{keyword 2}, keyword 3, keyword 4, keyword 5, keyword 6, keyword 7}
\end{abstract}

\section{First Level Heading}
Please lay out your article using the section headings and example objects below, and remember to delete all help text prior to submitting your article to the journal.

\begin{figure}[bt]
\centering
\includegraphics[width=6cm]{example-image-rectangle}
\caption{Although we encourage authors to send us the highest-quality figures possible, for peer-review purposes we are can accept a wide variety of formats, sizes, and resolutions. Legends should be concise but comprehensive – the figure and its legend must be understandable without reference to the text. Include definitions of any symbols used and define/explain all abbreviations and units of measurement.}
\end{figure}

\subsection{Second Level Heading}
If data, scripts or other artefacts used to generate the analyses presented in the article are available via a publicly available data repository, please include a reference to the location of the material within the article.

% Equations should be inserted using standard LaTeX equation and eqnarray environments, not as graphics, and should be set in the main text
This is an equation, numbered
\begin{equation}
\int_0^{+\infty}e^{-x^2}dx=\frac{\sqrt{\pi}}{2}
\end{equation}
And one that is not numbered
\begin{equation*}
e^{i\pi}=-1
\end{equation*}

\subsection{Adding Citations and a References List}

Please use a \verb|.bib| file to store your references. When using Overleaf to prepare your manuscript, you can upload a \verb|.bib| file or import your Mendeley, CiteULike or Zotero library directly as a \verb|.bib| file\footnote{see \url{https://www.overleaf.com/blog/184}}. You can then cite entries from it, like this: \cite{lees2010theoretical}. Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.

You can find a video tutorial here to learn more about BibTeX: \url{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}.

This template provides two options for the citation and reference list style: 
\begin{description}
\item[Numerical style] Use \verb|\documentclass[...,num-refs]{wiley-article}|
\item[Author-year style] Use \verb|\documentclass[...,alpha-refs]{wiley-article}|
\end{description}

\subsubsection{Third Level Heading}
Supporting information will be included with the published article. For submission any supporting information should be supplied as separate files but referred to in the text.

Appendices will be published after the references. For submission they should be supplied as separate files but referred to in the text.

\paragraph{Fourth Level Heading}
% Here are examples of quotes and epigraphs.
\begin{quote}
The significant problems we have cannot be solved at the same level of thinking with which we created them.\endnote{Albert Einstein said this.}
\end{quote}

\begin{epigraph}{Albert Einstein}
Anyone who has never made a mistake has never tried anything new.
\end{epigraph}

\subparagraph{Fifth level heading}
Measurements should be given in SI or SI-derived units.
Chemical substances should be referred to by the generic name only. Trade names should not be used. Drugs should be referred to by their generic names. If proprietary drugs have been used in the study, refer to these by their generic name, mentioning the proprietary name, and the name and location of the manufacturer, in parentheses.

\begin{table}[bt]
\caption{This is a table. Tables should be self-contained and complement, but not duplicate, information contained in the text. They should be not be provided as images. Legends should be concise but comprehensive – the table, legend and footnotes must be understandable without reference to the text. All abbreviations must be defined in footnotes.}
\begin{threeparttable}
\begin{tabular}{lccrr}
\headrow
\thead{Variables} & \thead{JKL ($\boldsymbol{n=30}$)} & \thead{Control ($\boldsymbol{n=40}$)} & \thead{MN} & \thead{$\boldsymbol t$ (68)}\\
Age at testing & 38 & 58 & 504.48 & 58 ms\\
Age at testing & 38 & 58 & 504.48 & 58 ms\\
Age at testing & 38 & 58 & 504.48 & 58 ms\\
Age at testing & 38 & 58 & 504.48 & 58 ms\\
\hiderowcolors
stop alternating row colors from here onwards\\
Age at testing & 38 & 58 & 504.48 & 58 ms\\
Age at testing & 38 & 58 & 504.48 & 58 ms\\
\hline  % Please only put a hline at the end of the table
\end{tabular}

\begin{tablenotes}
\item JKL, just keep laughing; MN, merry noise.
\end{tablenotes}
\end{threeparttable}
\end{table}

\section*{acknowledgements}
Acknowledgements should include contributions from anyone who does not meet the criteria for authorship (for example, to recognize contributions from people who provided technical help, collation of data, writing assistance, acquisition of funding, or a department chairperson who provided general support), as well as any funding or other support information.

\section*{conflict of interest}
You may be asked to provide a conflict of interest statement during the submission process. Please check the journal's author guidelines for details on what to include in this section. Please ensure you liaise with all co-authors to confirm agreement with the final statement.

\printendnotes

% Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.
\bibliography{sample}

\begin{biography}[example-image-1x1]{A.~One}
Please check with the journal's author guidelines whether author biographies are required. They are usually only included for review-type articles, and typically require photos and brief biographies (up to 75 words) for each author.
\bigskip
\bigskip
\end{biography}

\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}

\end{document}

### 2019-05-09 manuscript/journal-applied-entomology/main.tex
updated manuscript sections

@@
 
-\section{First Level Heading}
+\section{Introduction}
 Please lay out your article using the section headings and example objects below, and remember to delete all help text prior to submitting your article to the journal.
+
+\section{Materials and Methods}
+
+Camila Enter information here:....
+
+\section{Results}
+
+\section{Discussion}
 
@@
 
-\section*{acknowledgements}
+\section*{Acknowledgements}
 Acknowledgements should include contributions from anyone who does not meet the criteria for authorship (for example, to recognize contributions from people who provided technical help, collation of data, writing assistance, acquisition of funding, or a department chairperson who provided general support), as well as any funding or other support information.
 
-\section*{conflict of interest}
+\section*{Conflict of Interest}
 You may be asked to provide a conflict of interest statement during the submission process.
@@
 Please ensure you liaise with all co-authors to confirm agreement with the final statement.
+
+\section*{Author Contribution}
+
+\section*{Data Availability Statement}
 

### 2019-05-14 manuscript/journal-applied-entomology/main.tex
Added in figures and captions to manuscript.

@@
 % Include section in journal if known, otherwise delete
-\paperfield{Journal Section}
+%\paperfield{Journal Section}
 
@@
 \centering
-\includegraphics[width=6cm]{example-image-rectangle}
-\caption{Although we encourage authors to send us the highest-quality figures possible, for peer-review purposes we are can accept a wide variety of formats, sizes, and resolutions.
-Legends should be concise but comprehensive – the figure and its legend must be understandable without reference to the text.
-Include definitions of any symbols used and define/explain all abbreviations and units of measurement.}
+\includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
+\caption{Adult onion maggot fly catch on sticky traps of different shape.
+Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.
+Letters not shared between groups denote significant differences in female trap catch (there was no observed difference in male trap catch) at $\alpha$ = 0.05 with Tukey's HSD test.
+}
+\label{fig:figure1}
+\end{figure}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
+\caption{Adult onion maggot fly catch on spherical sticky traps of different size.
+Points and error bars denote mean and 95\% confidence intervals respectively.
+Letters not shared between groups indicates significant differences in adult catch at $\alpha$ = 0.05 with Tukey's HSD test.}
+\label{fig:figure2}
+\end{figure}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
+\caption{Adult onion maggot fly catch on spherical sticky traps of different color.
+Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
+\textbf{*} indicates significantly different trap catch on white sticky traps (P = 0.012).}
+\label{fig:figure3}
+\end{figure}
+
+\begin{figure}[bt]
+\centering
+\includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
+\caption{Adult onion maggot fly catch on sticky traps baited with Delia Lure attractant and unbaited.
+Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
+\textbf{*} indicates significantly different trap catch on baited and unbaited traps (P = 0.030).
+}
+\label{fig:figure4}
 \end{figure}

### 2019-05-14 manuscript/journal-applied-entomology/main.tex
added data management section to methods.

@@
 \section{Results}
+
+\subsection{Data Management and Analysis}
+
+All data for the trials were entered into flat tabular (.csv) files.
+All analysis on the raw data was conducted in R version 3.5.2 using RStudio as an IDE (with Vim keybindings) \citep{rcore2018,rstudio}.
+The $tidyverse$, $car$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, emmeans}.
+All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-attraction)
 

### 2019-05-15 manuscript/journal-applied-entomology/main.tex
Updated data methods and analysis section.

@@
 
-\section{Results}
+\subsection{Analysis}
 
-\subsection{Data Management and Analysis}
+Raw data from shape, size, and color trials were analyzed using linear models and analysis of variance.
+Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
+Based on these considerations, an outlier was detected and removed from the shape trials (P = 0.032, Bonferroni Outlier Test) and data from the size and color trials were square root transformed to conform with assumptions of normality and homoscedasticity.
+
+Raw data from the Delia Lure Trial were analyzed with a paired t-test due to the nature of the experimental design.
+Conformation to assumptions of normality were confirmed through examination of quantile-quantile plots.
+
+\subsection{Data Management}
 
@@
 The $tidyverse$, $car$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, emmeans}.
-All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-attraction)
+All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-attraction).
+
+\section{Results}
 

### 2019-05-15 manuscript/journal-applied-entomology/main.tex
methods updates

@@
 
-Camila Enter information here:....
+To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in Upstate New York.
+Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure attractant to evaluate potential improvement in trap catch.
+
+All trials were conducted in commercial fields on muck soil near Elba, NY in western upstate New York (\textbf{GPS coordinates, other information about unique muck characteristics?}).
+No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2011integrated}), the primary target of which is \textit{Thrips tabaci}.
+This management is unlikely to affect \textit{D.
+antiqua} populations due to spray timing and minimal impacts of thrips sprays on onion maggot fly \citep{finch1986behavior}.
+
+\subsection{Shape Trial}
+
+To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with sticky material (\textbf{Tanglefoot?}) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
+Traps were spaced 15.24 meters apart and arranged in a randomized control block design with five replications.
+Traps were placed in the field in late May then collected in late June (\textbf{Not sure about this, more info needed?}).
 

### 2019-05-16 manuscript/journal-applied-entomology/main.tex
Updated results section.

@@
 \section{Introduction}
-Please lay out your article using the section headings and example objects below, and remember to delete all help text prior to submitting your article to the journal.
+Coming Soon...
 
@@
 
-All trials were conducted in commercial fields on muck soil near Elba, NY in western upstate New York (\textbf{GPS coordinates, other information about unique muck characteristics?}).
+All shape, size, and color trials were conducted in commercial fields on muck soil near Elba, NY in western upstate New York (\textbf{GPS coordinates, other information about unique muck characteristics?}).
+Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in western upstate New York.
 No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2011integrated}), the primary target of which is \textit{Thrips tabaci}.
@@
 
-\subsection{Shape Trial}
+\subsection{Field Trials}
 
-To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with sticky material (\textbf{Tanglefoot?}) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
+\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with sticky material (\textbf{Tanglefoot?}) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
 Traps were spaced 15.24 meters apart and arranged in a randomized control block design with five replications.
 Traps were placed in the field in late May then collected in late June (\textbf{Not sure about this, more info needed?}).
+
+\paragraph{Size Trial}
+To evaluate the influence of trap size on the trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm diameter were placed along the long edge of onion fields with spacing 15.24 meters apart in a randomized controlled block design with five replications.
+
+\paragraph{Color Trial}
+To evaluate the effect of color on trap catch and monitoring of adult onion maggot fly, white, yellow, green, and red spherical sticky traps 8.75 cm in diameter were placed along the long edge of onion fields in a randomized controlled block design with five replications.
+
+\paragraph{Delia Lure Trial}
+To evaluate the effect of adding an attractant an trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
+Trap Catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.
 
@@
 
-\section{Discussion}
+\paragraph{Shape Trial} Models relating trap shape and \textit{D.
+antiqua} sex to trap catch significantly explained approximately 70\% of observed variation (P \textless 0.001, $R^2_{adj}$ = 0.70, Table \ref{table:1}).
+Trap shape significantly influenced (P = 0.005) catch of adult \textit{D.
+antiqua} (Figure \ref{fig:figure1}).
+Sticky traps caught approximately 27.81 $\pm$ 2.8 more female flies than male flies.
+Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.
+No significant differences were observed between male trap catch.
+
+\begin{table}[]
+\caption{Linear model and analysis of variance results and diagnostics for shape, size, and color trials.
+Treatment refers to the factor under evaluation.
+For the shape trial, treatment denotes shape; for the size trial, treatment denotes size; for the color trial, treatment denotes color.
+Missing values indicate that factor was not included in the best fit model.
+All code and additional documentation is available on GitHub.
+}
+\begin{tabular}{lrrrrrrrrr}
+              & \multicolumn{9}{c}{Trial}                                                                                                                                                                                                \\ \cline{2-10}
+              & \multicolumn{3}{c}{Shape}                                              & \multicolumn{3}{c}{Size}                                               & \multicolumn{3}{c}{Color}                                              \\
+              & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} \\ \cline{2-10}
+Sex           & 42                    & 1                      & \textless 0.0001      & 197.5                 & 1                      & \textless 0.0001      & 37.2                  & 1                      & \textless 0.0001      \\
+Treatment     & 4.4                   & 4                      & 0.005                 & 11.6                  & 4                      & \textless 0.0001      & 31.3                  & 3                      & \textless 0.0001      \\
+Year          &                       &                        &                       & 142.4                 & 1                      & \textless 0.0001      &                       &                        &                       \\
+Sex:Treatment &                       &                        &                       &                       &                        &                       & 6.3                   & 3                      & 0.002                 \\
+Sex:Year      &                       &                        &                       & 137.9                 & 1                      & \textless 0.0001      &                       &                        &                       \\ \cline{2-10}
+              &                       &                        &                       &                       &                        &                       &                       &                        &                       \\
+$R^2$            &                       &                        & 0.75                  &                       &                        & 0.75                  &                       &                        & 0.83                  \\
+$R^2_{adj}$         &                       &                        & 0.70                  &                       &                        & 0.73                  &                       &                        & 0.79                  \\
+P             &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001
+\end{tabular}
+\label{table:1}
+\end{table}
+
+\paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.73, Table \ref{table:1}).
+Trap size significantly influenced trap catch (P \textless 0.001).
+Increasing diameter of trap size showed a trend towards increasing trap catch (Figure \ref{fig:figure2}) with the largest trap catching significantly more females and males.
+
+\paragraph{Color Trial} Models using color and sex to explain observed trap catch significantly explained approximately 79\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.79, Table \ref{table:1}).
+Color significantly influenced trap catch (P \textless 0.001) with white traps catching significantly more females than any other color (t \textless -3.1, df = 32, P \textless 0.012) and significantly more males than any other color except yellow (t \textless -3.1, df = 32, P \textless 0.012, Yellow: t = -1.6, df = 32, P = 0.3).
+White traps caught significantly more females than males (t = 6.1, df = 32, P \textless 0.001).
+
+\paragraph{Delia Lure Trial} Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adult flies than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
 
@@
 
-\subsection{Second Level Heading}
-If data, scripts or other artefacts used to generate the analyses presented in the article are available via a publicly available data repository, please include a reference to the location of the material within the article.
-
-% Equations should be inserted using standard LaTeX equation and eqnarray environments, not as graphics, and should be set in the main text
-This is an equation, numbered
-\begin{equation}
-\int_0^{+\infty}e^{-x^2}dx=\frac{\sqrt{\pi}}{2}
-\end{equation}
-And one that is not numbered
-\begin{equation*}
-e^{i\pi}=-1
-\end{equation*}
-
-\subsection{Adding Citations and a References List}
-
-Please use a \verb|.bib| file to store your references.
-When using Overleaf to prepare your manuscript, you can upload a \verb|.bib| file or import your Mendeley, CiteULike or Zotero library directly as a \verb|.bib| file\footnote{see \url{https://www.overleaf.com/blog/184}}.
-You can then cite entries from it, like this: \cite{lees2010theoretical}.
-Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.
-
-You can find a video tutorial here to learn more about BibTeX: \url{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}.
-
-This template provides two options for the citation and reference list style: 
-\begin{description}
-\item[Numerical style] Use \verb|\documentclass[...,num-refs]{wiley-article}|
-\item[Author-year style] Use \verb|\documentclass[...,alpha-refs]{wiley-article}|
-\end{description}
-
-\subsubsection{Third Level Heading}
-Supporting information will be included with the published article. For submission any supporting information should be supplied as separate files but referred to in the text.
-
-Appendices will be published after the references. For submission they should be supplied as separate files but referred to in the text.
-
-\paragraph{Fourth Level Heading}
-% Here are examples of quotes and epigraphs.
-\begin{quote}
-The significant problems we have cannot be solved at the same level of thinking with which we created them.\endnote{Albert Einstein said this.}
-\end{quote}
-
-\begin{epigraph}{Albert Einstein}
-Anyone who has never made a mistake has never tried anything new.
-\end{epigraph}
-
-\subparagraph{Fifth level heading}
-Measurements should be given in SI or SI-derived units.
-Chemical substances should be referred to by the generic name only.
-Trade names should not be used.
-Drugs should be referred to by their generic names.
-If proprietary drugs have been used in the study, refer to these by their generic name, mentioning the proprietary name, and the name and location of the manufacturer, in parentheses.
-
-\begin{table}[bt]
-\caption{This is a table.
-Tables should be self-contained and complement, but not duplicate, information contained in the text.
-They should be not be provided as images.
-Legends should be concise but comprehensive – the table, legend and footnotes must be understandable without reference to the text.
-All abbreviations must be defined in footnotes.}
-\begin{threeparttable}
-\begin{tabular}{lccrr}
-\headrow
-\thead{Variables} & \thead{JKL ($\boldsymbol{n=30}$)} & \thead{Control ($\boldsymbol{n=40}$)} & \thead{MN} & \thead{$\boldsymbol t$ (68)}\\
-Age at testing & 38 & 58 & 504.48 & 58 ms\\
-Age at testing & 38 & 58 & 504.48 & 58 ms\\
-Age at testing & 38 & 58 & 504.48 & 58 ms\\
-Age at testing & 38 & 58 & 504.48 & 58 ms\\
-\hiderowcolors
-stop alternating row colors from here onwards\\
-Age at testing & 38 & 58 & 504.48 & 58 ms\\
-Age at testing & 38 & 58 & 504.48 & 58 ms\\
-\hline  % Please only put a hline at the end of the table
-\end{tabular}
-
-\begin{tablenotes}
-\item JKL, just keep laughing; MN, merry noise.
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
+\section{Discussion}
 
@@
 % Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.
-\bibliography{sample}
-
-\begin{biography}[example-image-1x1]{A.~One}
-Please check with the journal's author guidelines whether author biographies are required.
-They are usually only included for review-type articles, and typically require photos and brief biographies (up to 75 words) for each author.
-\bigskip
-\bigskip
-\end{biography}
 

### 2019-08-14 manuscript/journal-applied-entomology/main.tex
added introduction

@@
 
-\title{Camila Title Suggestions?}
+\title{Monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping}
 
 % List abbreviations here, if any. Please note that it is preferred that abbreviations be defined at the first instance they appear in the text, rather than creating an abbreviations list.
-\abbrevs{ABC, a black cat; DEF, doesn't ever fret; GHI, goes home immediately.}
+%\abbrevs{ABC, a black cat; DEF, doesn't ever fret; GHI, goes home immediately.}
 
@@
 Usually start with 1 for notes about author contributions; then continuing with 2 etc if any author has a different present address.
-\author[1\authfn{1}]{Author One PhD}
-\author[2\authfn{1}]{Author A.~Two MD}
-\author[2\authfn{2}]{Author Three PhD}
-\author[2]{Author B.~Four}
+\author[1\authfn{1}]{Denis S. Willett}
+\author[1\authfn{1}]{Camila C. Filgueiras}
+\author[2]{Starker Wright}
+\author[1]{Jan P. Nyrop}
+\author[1]{Brian A. Nault}
 
@@
 % Include full affiliation details for all authors
-\affil[1]{Department, Institution, City, State or Province, Postal Code, Country}
-\affil[2]{Department, Institution, City, State or Province, Postal Code, Country}
+\affil[1]{Department of Entomology, Cornell AgriTech, Cornell University, Geneva, NY, 14456, USA}
+\affil[2]{Bartlett Tree Experts, Dublin, PA, USA}
 
-\corraddress{Author One PhD, Department, Institution, City, State or Province, Postal Code, Country}
-\corremail{correspondingauthor@email.com}
-
-\presentadd[\authfn{2}]{Department, Institution, City, State or Province, Postal Code, Country}
-
-\fundinginfo{Funder One, Funder One Department, Grant/Award Number: 123456, 123457 and 123458; Funder Two, Funder Two Department, Grant/Award Number: 123459}
+\corraddress{Denis S. Willett, 15 Castle Creek Drive, Geneva, NY 14456}
+\corremail{deniswillett@cornell.edu}
 
 % Include the name of the author that should appear in the running header
-\runningauthor{Author One et al.}
+\runningauthor{Willett et al.}
 
@@
 \section{Introduction}
-Coming Soon...
+
+The onion maggot (\textit{Delia antiqua}) is a economically important pest of Allium crops worldwide.
+Found primarily in temperate climates, \textit{D.
+antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on Onions (\textit{Allium cepa} L.), Garlic (\textit{Allium sativem} L.), Scallions (\textit{Allium fistulosum} L.), and Chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
+Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where resistant populations have developed \citep{martinson1988dispersal, nault2006onion}.
+
+Onion maggot is a important pest in part due to its lifecycle.
+It is multivoltine with three generations per year in the Northern United States \citep{eckenrode1975population, hoepting2004insecticide}.
+Larvae feed on plant roots and allium bulbs causing the damage associated with this pest.
+First generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
+In addition, damaged plants become more susceptible to infestation by subsequent generations, pathogens, and damage at harvest time \citep{eckenrode1986impact,nault2006performance}.
+Even if plants are not completely killed by onion maggot larvae, feeding damage often renders the produce unmarketable.
+
+Management of this pest has relied on in-furrow insecticide application at planting \citep{nault2006performance}.
+A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
+Chlorpyrifos is commonly used as a drench treatment currently in combination with a cyromazine seed treatment \citep{nault2006performance}.
+Fipronil and spinosad are being considered as effective alternatives as some onion maggot populations are developing resistance to chlorpyrifos \citep{nault2006onion}.
+Cultural practices such as rotation, removal of damaged onions, and delayed planting remain effective management alternatives \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
+
+Delayed planting can be an effective control tactic because onion development if offset phenologically from development of onion maggot oviposition and larval development \citep{nault2011delaying}.
+Such tactics, and effective control in general, rely on monitoring onion maggot populations in the field.
+While useful in areas where onion maggot populations are already established, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.
+
+Past efforts at monitoring and understanding onion maggot population dynamics have relied on three principle methods: sticky traps, water traps, and simulation.
+Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.
+Trap catch of adult onion maggot flies can be low compared to field populations.
+Additionally, the number of onion maggots caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.
+Odor sources of attractants have also been added to traps in an effort to make them more attractive, but with limited success.
+Simulation has relied on field data from traps, phenological studies in the lab, and climate information \citep{thomingdeveloping,otto2000development,ning2017predicting}.
+Population simulations can prove useful at larger scales, but often lack extremely detailed location specific information necessary for producers to determine if they have a severe problem in a specific field.
+
+To further develop effective monitoring methodologies for the onion maggot, we evaluated a number of factors likely to influence attraction of adult onion maggot flies.
+Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult onion maggots \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
+We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate monitoring potential and efficacy.
 
@@
 
-To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in Upstate New York.
+To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
 Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure attractant to evaluate potential improvement in trap catch.
 
-All shape, size, and color trials were conducted in commercial fields on muck soil near Elba, NY in western upstate New York (\textbf{GPS coordinates, other information about unique muck characteristics?}).
+All shape, size, and color trials were conducted in commercial dry bulb onion fields on muck soil near Elba, NY in western upstate New York.
+Muck soils are high-organic matter soils formed from old lake beds.
 Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in western upstate New York.
+All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high onion maggot populations.
 No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2011integrated}), the primary target of which is \textit{Thrips tabaci}.
@@
 Traps were spaced 15.24 meters apart and arranged in a randomized control block design with five replications.
-Traps were placed in the field in late May then collected in late June (\textbf{Not sure about this, more info needed?}).
+Traps were placed in the field in late May then collected in late June.
 
@@
 
-\printendnotes
+%\printendnotes
 
 % Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.
+
+\section{References}
+
+\bibliographystyle{vancouver-authoryear}
+\bibliography{om-attraction}
 

### 2019-08-14 manuscript/journal-applied-entomology/main.tex
first draft

@@
 \usepackage{siunitx}
+\usepackage{lineno}
 
@@
 \begin{abstract}
-This is a generic template designed for use by multiple journals, which includes several options for customization.
-Please consult the author guidelines for the journal to which you are submitting in order to confirm that your manuscript will comply with the journal's requirements.
-Please replace this text with your abstract.
+Onion maggot (\textit{Delia antiqua}) is an economically important pest of alliums in temperate regions throughout the world.
+Management of this pest is necessary to achieve economic returns and depends on insecticide regimes and cultural management.
+Both means of control rely upon effective monitoring of \textit{D.
+antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of adult onion maggot flies to accurately reflect population dynamics.
+We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult onion maggot flies in upstate New York.
+White, large diameter, spherical traps in conjunction with Delia Lure performed the best in attracting and catching onion maggot adults.
+These results suggest an improved means of monitoring onion maggot populations which will be useful in informing modeling and monitoring efforts especially in areas where onion maggot is an emergent pest.
 
 % Please include a maximum of seven keywords
-\keywords{keyword 1, \emph{keyword 2}, keyword 3, keyword 4, keyword 5, keyword 6, keyword 7}
+\keywords{Onion Maggot, \textit{Delia antiqua}, attraction, sticky-trap, attract-and-kill, lure, onion management}
 \end{abstract}
 
+\linenumbers
 \section{Introduction}
@@
 To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
-Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure attractant to evaluate potential improvement in trap catch.
+Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (\textbf{Company Info here - is this ChemTica?}) attractant to evaluate potential improvement in trap catch.
 
@@
 Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.
+While there were no significant differences between females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.
 No significant differences were observed between male trap catch.
@@
 Increasing diameter of trap size showed a trend towards increasing trap catch (Figure \ref{fig:figure2}) with the largest trap catching significantly more females and males.
+While male trap catch was less than that of females, trends in catch amoung the different diameters were similar for both males and females.
 
@@
 
-\paragraph{Delia Lure Trial} Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adult flies than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
+\paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult onion maggot flies.
+Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adult flies than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
 
@@
 
+Varying the shape, size and color of sticky traps revealed that changes in these factors can increase catch of adult onion maggot flies.
+Short cylinder traps performed better than most other shapes and were not significantly different from spherical traps.
+Spherical traps were more economical to produce and use so they were selected for use in subsequent studies.
+Size played a large role in increasing trap catch.
+Larger diameter traps with more surface area captured more adult onion maggot flies.
+Color had perhaps the largest impact on catch of adult onion maggot flies with white traps far outperforming yellow, green and red traps.
+
+The combination of sticky traps with the attractive Delia Lure also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
+Our work suggests that all of these factors play a role in onion maggot attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in onion maggot attraction \citep{harris1988host}.
+
+Sticky traps were chosen for this study in lieu of water traps because of their ease of use (replacing water is not necessary, and rain is not a problem) and because previous work has shown them to be more effective that water pan traps at catching onion maggot adults \citep{thomingdeveloping}.
+This work showed that white traps far outperform sticky traps of other colors confirming findings in another study that white traps work well for \textit{Delia} flies.
+Interestingly, other work has suggested that specificity for \textit{D.
+antiqua} could be improved with the color blue, but that overal trap catch may suffer \citep{thomingdeveloping}.
+
+These results suggest a way forward in improving monitoring ability of onion maggot fly adults in the field.
+A spherical, white, large diameter stick trap baited with Delia Lure is the best option for monitoring adult onion maggot flies out of the various factors tested in these trials.
+Accurate monitoring of onion maggot populations better informs producers about pest management challenges, especially in areas where onion maggot is an emergent pest.
+Additionally, more accurate measurements of population dynamics can inform modeling efforts and predictive management abilities \cite{ning2017predicting, otto2000development,thomingdeveloping}.
+
+The ability to attract larger numbers of adult onion maggot flies also opens the possibility for a different, more environmentally friendly, management method.
+If larger number of flies can be attracted then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be controlled.
+'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.
+Using large, white, spherical traps in conjunction with Delia Lure may provide the attraction needed to make it possible to control these pests using attract and kill strategies.
+
 \section*{Acknowledgements}
-Acknowledgements should include contributions from anyone who does not meet the criteria for authorship (for example, to recognize contributions from people who provided technical help, collation of data, writing assistance, acquisition of funding, or a department chairperson who provided general support), as well as any funding or other support information.
+Suggestions for acknowledgements?
 
 \section*{Conflict of Interest}
-You may be asked to provide a conflict of interest statement during the submission process.
-Please check the journal's author guidelines for details on what to include in this section.
-Please ensure you liaise with all co-authors to confirm agreement with the final statement.
+The authors declare no conflict of interest.
 
 \section*{Author Contribution}
+BAN, JPN, and SW designed the experiments.  DSW, CCF, and BAN analyzed the data and wrote the manuscript.
 
 \section*{Data Availability Statement}
+All code and data, including manuscript documentation, is available on GitHub(https://github.com/acetworld/onion-maggot-attraction).
 

### 2019-08-15 manuscript/journal-applied-entomology/main.tex
minor edits

@@
 
-\title{Monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping}
+\title{Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping}
 
@@
 We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult onion maggot flies in upstate New York.
-White, large diameter, spherical traps in conjunction with Delia Lure performed the best in attracting and catching onion maggot adults.
+White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching onion maggot adults.
 These results suggest an improved means of monitoring onion maggot populations which will be useful in informing modeling and monitoring efforts especially in areas where onion maggot is an emergent pest.
@@
 
-The onion maggot (\textit{Delia antiqua}) is a economically important pest of Allium crops worldwide.
+The onion maggot (\textit{Delia antiqua}) is an economically important pest of Allium crops worldwide.
 Found primarily in temperate climates, \textit{D.
@@
 
-Onion maggot is a important pest in part due to its lifecycle.
+Onion maggot is a primary pest in part due to its lifecycle.
 It is multivoltine with three generations per year in the Northern United States \citep{eckenrode1975population, hoepting2004insecticide}.
@@
 A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
-Chlorpyrifos is commonly used as a drench treatment currently in combination with a cyromazine seed treatment \citep{nault2006performance}.
-Fipronil and spinosad are being considered as effective alternatives as some onion maggot populations are developing resistance to chlorpyrifos \citep{nault2006onion}.
+Chlorpyrifos is commonly used as a drench treatment currently in combination with a Cyromazine seed treatment \citep{nault2006performance}.
+Fipronil and Spinosad are being considered as effective alternatives as some onion maggot populations are developing resistance to Chlorpyrifos \citep{nault2006onion}.
 Cultural practices such as rotation, removal of damaged onions, and delayed planting remain effective management alternatives \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.

### 2019-08-29 manuscript/journal-applied-entomology/main.tex
Updated with BAN comments

@@
 Found primarily in temperate climates, \textit{D.
-antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on Onions (\textit{Allium cepa} L.), Garlic (\textit{Allium sativem} L.), Scallions (\textit{Allium fistulosum} L.), and Chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
+antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on onions (\textit{Allium cepa} L.), garlic (\textit{Allium sativem} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
 Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where resistant populations have developed \citep{martinson1988dispersal, nault2006onion}.
@@
 Larvae feed on plant roots and allium bulbs causing the damage associated with this pest.
-First generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
-In addition, damaged plants become more susceptible to infestation by subsequent generations, pathogens, and damage at harvest time \citep{eckenrode1986impact,nault2006performance}.
+First-generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
+In addition, damaged plants become more susceptible to infestation by subsequent generations and pathogens \citep{eckenrode1986impact,nault2006performance}.
 Even if plants are not completely killed by onion maggot larvae, feeding damage often renders the produce unmarketable.
 
-Management of this pest has relied on in-furrow insecticide application at planting \citep{nault2006performance}.
+Management of this pest has relied on prophylactic insecticide applications at planting \citep{nault2006performance}.
 A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
-Chlorpyrifos is commonly used as a drench treatment currently in combination with a Cyromazine seed treatment \citep{nault2006performance}.
-Fipronil and Spinosad are being considered as effective alternatives as some onion maggot populations are developing resistance to Chlorpyrifos \citep{nault2006onion}.
-Cultural practices such as rotation, removal of damaged onions, and delayed planting remain effective management alternatives \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
+Chlorpyrifos is commonly used as a drench treatment in combination with either cyromazine seed treatment (Trigard)  \citep{nault2006performance} or the seed treatment package containing thiamethoxam, spinosad and several fungicides (FarMore FI500).
+Cultural practices such as crop rotation, removal of damaged onions, and delayed planting are also effective management tactics \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
 
-Delayed planting can be an effective control tactic because onion development if offset phenologically from development of onion maggot oviposition and larval development \citep{nault2011delaying}.
-Such tactics, and effective control in general, rely on monitoring onion maggot populations in the field.
-While useful in areas where onion maggot populations are already established, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.
+In situations where an insecticide application at planting is not desired for onion maggot control, reliance on monitoring onion maggot adult activity in the field can be important for deploying curative management tactics.
+Additionally, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.
 
-Past efforts at monitoring and understanding onion maggot population dynamics have relied on three principle methods: sticky traps, water traps, and simulation.
+Past efforts at monitoring and understanding onion maggot population dynamics have relied on three principal methods: sticky traps, water traps, and simulation.
 Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.
@@
 Additionally, the number of onion maggots caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.
-Odor sources of attractants have also been added to traps in an effort to make them more attractive, but with limited success.
+Odor sources of attractants also have been added to traps in an effort to make them more attractive, but with limited success.
 Simulation has relied on field data from traps, phenological studies in the lab, and climate information \citep{thomingdeveloping,otto2000development,ning2017predicting}.
@@
 To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
-Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (\textbf{Company Info here - is this ChemTica?}) attractant to evaluate potential improvement in trap catch.
+Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (AgBio, Westminster, CO) attractant to evaluate potential improvement in trap catch.
 
@@
 All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high onion maggot populations.
-No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2011integrated}), the primary target of which is \textit{Thrips tabaci}.
-This management is unlikely to affect \textit{D.
-antiqua} populations due to spray timing and minimal impacts of thrips sprays on onion maggot fly \citep{finch1986behavior}.
+No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2019}), the primary target of which is \textit{Thrips tabaci}.
+This management did affect \textit{D.
+antiqua} populations as spray timing and efficacy of products targeting thrips have minimal to no impact on onion maggot fly \citep{finch1986behavior}.
 
@@
 
-\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with sticky material (\textbf{Tanglefoot?}) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
-Traps were spaced 15.24 meters apart and arranged in a randomized control block design with five replications.
-Traps were placed in the field in late May then collected in late June.
+For all field trials, numbers of male and female \textit{D. antiqua} flies were recorded weekly from traps beginning in late May and ending in late June.
+
+\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with Tanglefoot sticky material (The Scotts Company LLC, Maryville, OH) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
+Traps were spaced 15.2 meters apart and arranged in a randomized control block design with five replications.
 
 \paragraph{Size Trial}
-To evaluate the influence of trap size on the trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm diameter were placed along the long edge of onion fields with spacing 15.24 meters apart in a randomized controlled block design with five replications.
+To evaluate the influence of trap size on trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm were placed along the long edge of onion fields with spacing 15.2 meters apart in a randomized controlled block design with five replications.
 
@@
 \paragraph{Delia Lure Trial}
-To evaluate the effect of adding an attractant an trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
-Trap Catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.
+To evaluate the effect of adding a chemical attractant to enhance trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
+Trap catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.
 
@@
 antiqua} (Figure \ref{fig:figure1}).
-Sticky traps caught approximately 27.81 $\pm$ 2.8 more female flies than male flies.
+Sticky traps caught approximately 27.8 $\pm$ 2.8 more females than males.
 Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.
-While there were no significant differences between females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.
-No significant differences were observed between male trap catch.
+While there were no significant differences between numbers of females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.
+No significant differences were observed among treatments for male trap catch.
 
@@
 \paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.73, Table \ref{table:1}).
+Numbers of females captured were significantly greater than numbers of males, especially in 2005.
 Trap size significantly influenced trap catch (P \textless 0.001).
 Increasing diameter of trap size showed a trend towards increasing trap catch (Figure \ref{fig:figure2}) with the largest trap catching significantly more females and males.
-While male trap catch was less than that of females, trends in catch amoung the different diameters were similar for both males and females.
+While male trap catch was less than that of females, trends in catch among the different diameters were similar for both males and females.
 
@@
 \paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult onion maggot flies.
-Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adult flies than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
+Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adults than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
 
@@
 \includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
-\caption{Adult onion maggot fly catch on sticky traps of different shape.
+\caption{Adult onion maggot fly catch per trap over the sampling period on sticky traps of different shape.
 Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.
@@
 \includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
-\caption{Adult onion maggot fly catch on spherical sticky traps of different size.
+\caption{Adult onion maggot fly catch per trap over the sampling period on spherical sticky traps of different size.
 Points and error bars denote mean and 95\% confidence intervals respectively.
@@
 \includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
-\caption{Adult onion maggot fly catch on spherical sticky traps of different color.
+\caption{Adult onion maggot fly catch per trap over the sampling period on spherical sticky traps of different color.
 Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
@@
 \includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
-\caption{Adult onion maggot fly catch on sticky traps baited with Delia Lure attractant and unbaited.
+\caption{Adult onion maggot fly catch per trap over the sampling period on sticky traps baited with Delia Lure attractant and unbaited.
 Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
@@
 
-The combination of sticky traps with the attractive Delia Lure also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
+The combination of sticky traps with the chemical attractant, Delia Lure, also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
 Our work suggests that all of these factors play a role in onion maggot attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in onion maggot attraction \citep{harris1988host}.
@@
 These results suggest a way forward in improving monitoring ability of onion maggot fly adults in the field.
-A spherical, white, large diameter stick trap baited with Delia Lure is the best option for monitoring adult onion maggot flies out of the various factors tested in these trials.
-Accurate monitoring of onion maggot populations better informs producers about pest management challenges, especially in areas where onion maggot is an emergent pest.
-Additionally, more accurate measurements of population dynamics can inform modeling efforts and predictive management abilities \cite{ning2017predicting, otto2000development,thomingdeveloping}.
+A spherical, white, large diameter sticky trap baited with Delia Lure is the best option for monitoring adult onion maggot flies based on the various factors tested in these trials.
+Accurate monitoring of onion maggot populations better informs producers about deploying curative pest management tactics, as well as provides a means for identifying where onion maggot is an emergent pest.
+Additionally, more accurate measurements of population dynamics can inform modeling efforts and predictive management abilities \citep{ning2017predicting, otto2000development,thomingdeveloping}.
 
-The ability to attract larger numbers of adult onion maggot flies also opens the possibility for a different, more environmentally friendly, management method.
-If larger number of flies can be attracted then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be controlled.
+Sticky traps have been used in monitoring and control efforts of other visually responsive flies.
+Orange spheres have been effective at attracting and trapping Caribbean Fruit Fly (\textit{Anastrepha suspensa} Lowe) \citep{sivinski1990colored}.
+Apple maggot (\textit{Rhagoletis pomonella} Walsh) management, in particular, has benefited from development of red spherical traps for monitoring field populations \citep{prokopy1975apple, drummond1984comparative, duan1994apple}.
+This work has even expanded into control methods with trapping using these spheres reducing pest populations and used in conjunction with other strategies \citep{bostanian1999managing}.
+
+The ability to attract larger numbers of adult onion maggot flies also creates an opportunity for a different, more environmentally friendly, management method.
+If larger numbers of flies can be attracted and then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be reduced.
 'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.
@@
 \section*{Acknowledgements}
-Suggestions for acknowledgements?
+We appreciate technical assistance by M. Hessney and Delia Lure from J. Meneley.
 

### 2019-09-24 manuscript/journal-applied-entomology/main.tex
More author comments

@@
 \author[1\authfn{1}]{Camila C. Filgueiras}
-\author[2]{Starker Wright}
 \author[1]{Jan P. Nyrop}
@@
 \affil[1]{Department of Entomology, Cornell AgriTech, Cornell University, Geneva, NY, 14456, USA}
-\affil[2]{Bartlett Tree Experts, Dublin, PA, USA}
 
@@
 White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching onion maggot adults.
-These results suggest an improved means of monitoring onion maggot populations which will be useful in informing modeling and monitoring efforts especially in areas where onion maggot is an emergent pest.
+These results suggest an improved means of attracting and capturing onion maggot populations which could be useful in monitoring efforts and development of attract and kill strategies for pest control.
 
@@
 antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on onions (\textit{Allium cepa} L.), garlic (\textit{Allium sativem} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
-Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where resistant populations have developed \citep{martinson1988dispersal, nault2006onion}.
+Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where populations resistant to insecticides have developed \citep{martinson1988dispersal, nault2006onion}.
 
@@
 
-Past efforts at monitoring and understanding onion maggot population dynamics have relied on three principal methods: sticky traps, water traps, and simulation.
+Past efforts at monitoring and understanding onion maggot phenology have relied on three principal methods: sticky traps, water traps, and simulation.
 Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.
@@
 Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult onion maggots \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
-We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate monitoring potential and efficacy.
+We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate ability to capture adult onion maggots.
 
@@
 No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2019}), the primary target of which is \textit{Thrips tabaci}.
-This management did affect \textit{D.
+This management did not affect \textit{D.
 antiqua} populations as spray timing and efficacy of products targeting thrips have minimal to no impact on onion maggot fly \citep{finch1986behavior}.
@@
 Interestingly, other work has suggested that specificity for \textit{D.
-antiqua} could be improved with the color blue, but that overal trap catch may suffer \citep{thomingdeveloping}.
+antiqua} could be improved with the color blue, but that overall trap catch may suffer \citep{thomingdeveloping}.
 
-These results suggest a way forward in improving monitoring ability of onion maggot fly adults in the field.
+These results suggest a way forward in improving trapping of onion maggot fly adults in the field.
 A spherical, white, large diameter sticky trap baited with Delia Lure is the best option for monitoring adult onion maggot flies based on the various factors tested in these trials.
-Accurate monitoring of onion maggot populations better informs producers about deploying curative pest management tactics, as well as provides a means for identifying where onion maggot is an emergent pest.
-Additionally, more accurate measurements of population dynamics can inform modeling efforts and predictive management abilities \citep{ning2017predicting, otto2000development,thomingdeveloping}.
+Improved trapping ability of white large diameter traps may improve monitoring efforts in situations where it is desirable to understand onion maggot phenology, develop decision support tools, measure range, and understand inter- and intra-generational spatio-temporal dynamics.
+This improved trapping could then inform modeling efforts and predictive management abilities \citep{ning2017predicting, otto2000development,thomingdeveloping}.
 
@@
 \section*{Acknowledgements}
-We appreciate technical assistance by M. Hessney and Delia Lure from J. Meneley.
+We appreciate technical assistance by M.
+Hessney and Delia Lure from J.
+Meneley.
+Starker Wright aided in development and construction of traps.
+The New York State Integrated Pest Management Program, USDA/CSREES Pest Management Alternatives Program, and New York State Department of Agriculture and Markets Onion Research and Development Program supported this research.
 
@@
 
-\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}
+%\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}
 

### 2019-10-01 manuscript/journal-applied-entomology/main.tex
final manuscript author feedback

@@
 \begin{abstract}
-Onion maggot (\textit{Delia antiqua}) is an economically important pest of alliums in temperate regions throughout the world.
+Onion maggot (\textit{Delia antiqua}) is an economically important pest of Allium crops in temperate regions throughout the world.
 Management of this pest is necessary to achieve economic returns and depends on insecticide regimes and cultural management.
-Both means of control rely upon effective monitoring of \textit{D.
-antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of adult onion maggot flies to accurately reflect population dynamics.
-We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult onion maggot flies in upstate New York.
-White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching onion maggot adults.
-These results suggest an improved means of attracting and capturing onion maggot populations which could be useful in monitoring efforts and development of attract and kill strategies for pest control.
+Future management strategies for \textit{D.
+antiqua} may rely upon effective monitoring of \textit{D.
+antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of \textit{D.
+antiqua} flies to accurately reflect population dynamics.
+We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult \textit{D.
+antiqua} flies in upstate New York.
+White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching \textit{D.
+antiqua} adults.
+These results suggest an improved means of attracting and capturing \textit{D.
+antiqua} populations which could be useful in monitoring efforts and development of attract and kill strategies for pest control.
 
@@
 
-The onion maggot (\textit{Delia antiqua}) is an economically important pest of Allium crops worldwide.
+The onion maggot (\textit{Delia antiqua} Meigen) is an economically important pest of Allium crops worldwide.
 Found primarily in temperate climates, \textit{D.
-antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on onions (\textit{Allium cepa} L.), garlic (\textit{Allium sativem} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
+antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on onions (\textit{Allium cepa} L.), garlic (\textit{Allium sativum} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
 Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where populations resistant to insecticides have developed \citep{martinson1988dispersal, nault2006onion}.
 
-Onion maggot is a primary pest in part due to its lifecycle.
+\textit{D.
+antiqua} is a primary pest in part due to its lifecycle.
 It is multivoltine with three generations per year in the Northern United States \citep{eckenrode1975population, hoepting2004insecticide}.
 Larvae feed on plant roots and allium bulbs causing the damage associated with this pest.
-First-generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
+First-generation infestations are particularly devastating as early feeding by \textit{D.
+antiqua} larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
 In addition, damaged plants become more susceptible to infestation by subsequent generations and pathogens \citep{eckenrode1986impact,nault2006performance}.
-Even if plants are not completely killed by onion maggot larvae, feeding damage often renders the produce unmarketable.
+Even if plants are not completely killed by \textit{D.
+antiqua} larvae, feeding damage often renders the bulbs unmarketable.
 
@@
 Chlorpyrifos is commonly used as a drench treatment in combination with either cyromazine seed treatment (Trigard)  \citep{nault2006performance} or the seed treatment package containing thiamethoxam, spinosad and several fungicides (FarMore FI500).
-Cultural practices such as crop rotation, removal of damaged onions, and delayed planting are also effective management tactics \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
+Cultural practices such as crop rotation, removal of cull and volunteer onions from fields, and delayed planting are also effective management tactics  \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
 
-In situations where an insecticide application at planting is not desired for onion maggot control, reliance on monitoring onion maggot adult activity in the field can be important for deploying curative management tactics.
-Additionally, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.
+In situations where an insecticide application at planting is not desired for \textit{D.
+antiqua} control, reliance on monitoring \textit{D.
+antiqua} adult activity in the field can be important for deploying curative management tactics.
+Additionally, effective monitoring becomes even more important where \textit{D.
+antiqua} is a relatively recent introduction or in areas where producers are not sure they have a problem.
 
-Past efforts at monitoring and understanding onion maggot phenology have relied on three principal methods: sticky traps, water traps, and simulation.
+Past efforts at monitoring and understanding \textit{D.
+antiqua} phenology have relied on three principal methods: sticky traps, water traps, and simulation.
 Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.
-Trap catch of adult onion maggot flies can be low compared to field populations.
-Additionally, the number of onion maggots caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.
+Trap catch of adult \textit{D.
+antiqua} flies can be low compared to field populations.
+Additionally, the number of \textit{D.
+antiqua} caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.
 Odor sources of attractants also have been added to traps in an effort to make them more attractive, but with limited success.
@@
 
-To further develop effective monitoring methodologies for the onion maggot, we evaluated a number of factors likely to influence attraction of adult onion maggot flies.
-Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult onion maggots \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
-We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate ability to capture adult onion maggots.
+To further develop effective monitoring methodologies for the \textit{D.
+antiqua}, we evaluated a number of factors likely to influence attraction of adult \textit{D.
+antiqua} flies.
+Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult \textit{D.
+antiqua} \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
+We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were evaluated to capture adult \textit{D.
+antiqua}.
 
@@
 
-To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
+To improve trap catch and monitoring of adult \textit{D.
+antiqua} flies, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
 Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (AgBio, Westminster, CO) attractant to evaluate potential improvement in trap catch.
@@
 Muck soils are high-organic matter soils formed from old lake beds.
-Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in western upstate New York.
-All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high onion maggot populations.
+Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in central upstate New York.
+All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high \textit{D.
+antiqua} populations.
 No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2019}), the primary target of which is \textit{Thrips tabaci}.
 This management did not affect \textit{D.
-antiqua} populations as spray timing and efficacy of products targeting thrips have minimal to no impact on onion maggot fly \citep{finch1986behavior}.
+antiqua} populations as spray timing and efficacy of products targeting thrips have minimal to no impact on \textit{D.
+antiqua} adults \citep{finch1986behavior}.
 
@@
 
-\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with Tanglefoot sticky material (The Scotts Company LLC, Maryville, OH) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
+\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult \textit{D.
+antiqua} flies, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with Tanglefoot sticky material (The Scotts Company LLC, Maryville, OH) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
 Traps were spaced 15.2 meters apart and arranged in a randomized control block design with five replications.
@@
 \paragraph{Size Trial}
-To evaluate the influence of trap size on trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm were placed along the long edge of onion fields with spacing 15.2 meters apart in a randomized controlled block design with five replications.
+To evaluate the influence of trap size on trap catch and monitoring of adult \textit{D.
+antiqua} flies, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm were placed along the long edge of onion fields with spacing 15.2 meters apart in a randomized controlled block design with five replications.
 
 \paragraph{Color Trial}
-To evaluate the effect of color on trap catch and monitoring of adult onion maggot fly, white, yellow, green, and red spherical sticky traps 8.75 cm in diameter were placed along the long edge of onion fields in a randomized controlled block design with five replications.
+To evaluate the effect of color on trap catch and monitoring of adult \textit{D.
+antiqua} flies, white, yellow, green, and red spherical sticky traps 8.75 cm in diameter were placed along the long edge of onion fields in a randomized controlled block design with five replications.
 
 \paragraph{Delia Lure Trial}
-To evaluate the effect of adding a chemical attractant to enhance trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
+To evaluate the effect of adding a chemical attractant to enhance trap catch and monitoring of adult \textit{D.
+antiqua} flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
 Trap catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.
@@
 Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
-Based on these considerations, an outlier was detected and removed from the shape trials (P = 0.032, Bonferroni Outlier Test) and data from the size and color trials were square root transformed to conform with assumptions of normality and homoscedasticity.
+Based on these considerations, an outlier was detected and removed from the shape trial (P = 0.032, Bonferroni Outlier Test) and data from the size and color trials were square root transformed to conform with assumptions of normality and homoscedasticity.
 
@@
 
-\paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult onion maggot flies.
+\paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult \textit{D.
+antiqua} flies.
 Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adults than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
@@
 \includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on sticky traps of different shape.
+\caption{\textit{D.
+antiqua} fly catch per trap over the sampling period on sticky traps of different shape.
 Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.
@@
 \includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on spherical sticky traps of different size.
+\caption{\textit{D.
+antiqua} fly catch per trap over the sampling period on spherical sticky traps of different size.
 Points and error bars denote mean and 95\% confidence intervals respectively.
@@
 \includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on spherical sticky traps of different color.
+\caption{\textit{D.
+antiqua} fly catch per trap over the sampling period on spherical sticky traps of different color.
 Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
@@
 \includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on sticky traps baited with Delia Lure attractant and unbaited.
+\caption{\textit{D.
+antiqua} fly catch per trap over the sampling period on sticky traps baited with Delia Lure attractant and unbaited.
 Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
@@
 
-Varying the shape, size and color of sticky traps revealed that changes in these factors can increase catch of adult onion maggot flies.
-Short cylinder traps performed better than most other shapes and were not significantly different from spherical traps.
+Varying the shape, size and color of sticky traps revealed that changes in these factors can increase catch of \textit{D.
+antiqua} flies.
+Short cylinder traps performed better than most other shapes, but were not significantly different from spherical traps.
 Spherical traps were more economical to produce and use so they were selected for use in subsequent studies.
 Size played a large role in increasing trap catch.
-Larger diameter traps with more surface area captured more adult onion maggot flies.
-Color had perhaps the largest impact on catch of adult onion maggot flies with white traps far outperforming yellow, green and red traps.
+Larger diameter traps with more surface area captured more adult \textit{D.
+antiqua} flies.
+Color had perhaps the largest impact on catch of adult \textit{D.
+antiqua} flies with white traps far outperforming yellow, green and red traps.
 
-The combination of sticky traps with the chemical attractant, Delia Lure, also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
-Our work suggests that all of these factors play a role in onion maggot attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in onion maggot attraction \citep{harris1988host}.
+The combination of sticky traps with the chemical attractant, Delia Lure, also increased catch of adult \textit{D.
+antiqua} flies suggesting that \textit{D.
+antiqua} adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
+Our work suggests that all of these factors play a role in \textit{D.
+antiqua} attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in \textit{D.
+antiqua} attraction \citep{harris1988host}.
 
-Sticky traps were chosen for this study in lieu of water traps because of their ease of use (replacing water is not necessary, and rain is not a problem) and because previous work has shown them to be more effective that water pan traps at catching onion maggot adults \citep{thomingdeveloping}.
+Sticky traps were chosen for this study in lieu of water traps because of their ease of use (replacing water is not necessary, and rain is not a problem) and because previous work has shown them to be more effective that water pan traps at catching \textit{D.
+antiqua} adults \citep{thomingdeveloping}.
 This work showed that white traps far outperform sticky traps of other colors confirming findings in another study that white traps work well for \textit{Delia} flies.
@@
 
-These results suggest a way forward in improving trapping of onion maggot fly adults in the field.
-A spherical, white, large diameter sticky trap baited with Delia Lure is the best option for monitoring adult onion maggot flies based on the various factors tested in these trials.
-Improved trapping ability of white large diameter traps may improve monitoring efforts in situations where it is desirable to understand onion maggot phenology, develop decision support tools, measure range, and understand inter- and intra-generational spatio-temporal dynamics.
+These results suggest a way forward in improving trapping of \textit{D.
+antiqua} fly adults in the field.
+A spherical, white, large diameter sticky trap baited with Delia Lure is the best option for monitoring adult \textit{D.
+antiqua} flies based on the various factors tested in these trials.
+Improved trapping ability of white large diameter traps may improve monitoring efforts in situations where it is desirable to understand \textit{D.
+antiqua} phenology, develop decision support tools, measure range, and understand inter- and intra-generational spatio-temporal dynamics.
 This improved trapping could then inform modeling efforts and predictive management abilities \citep{ning2017predicting, otto2000development,thomingdeveloping}.
@@
 Apple maggot (\textit{Rhagoletis pomonella} Walsh) management, in particular, has benefited from development of red spherical traps for monitoring field populations \citep{prokopy1975apple, drummond1984comparative, duan1994apple}.
-This work has even expanded into control methods with trapping using these spheres reducing pest populations and used in conjunction with other strategies \citep{bostanian1999managing}.
+This work has even expanded into a control method by trapping apple maggot flies using these spheres in conjunction with other strategies, which hasreduced infestations \citep{bostanian1999managing}.
 
-The ability to attract larger numbers of adult onion maggot flies also creates an opportunity for a different, more environmentally friendly, management method.
-If larger numbers of flies can be attracted and then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be reduced.
+The ability to attract larger numbers of adult \textit{D.
+antiqua} flies also creates an opportunity for a different, more environmentally friendly, management method.
+If larger numbers of flies can be attracted and then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of \textit{D.
+antiqua} could be reduced.
 'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.
@@
 Meneley.
-Starker Wright aided in development and construction of traps.
+Starker Wright aided in the development and construction of traps as well as experimental design.
 The New York State Integrated Pest Management Program, USDA/CSREES Pest Management Alternatives Program, and New York State Department of Agriculture and Markets Onion Research and Development Program supported this research.

### 2019-10-01 analysis/om_color_trials_2005.R
adjusted figures based on author feedback

@@ -74,18 +74,23 @@ jitter_width = 0.12
 set.seed(72)
 
 # generate figure
-color_trial_figure <- ggplot(color_trial_treatment, aes(x = color, y = flies, color = sex)) + 
+color_trial_figure <- ggplot(color_trial_treatment, 
+                             aes(x = color, y = flies, 
+                                 color = sex,
+                                 shape = sex)) + 
     stat_summary(fun.data = 'mean_cl_boot', 
                  geom = 'errorbar',
                  position = position_dodge(dodge_width),
-                 width = dodge_width/2) +
+                 width = dodge_width) +
     stat_summary(fun.data = 'mean_cl_boot',
-                 geom = 'point',
+                 geom = 'point', size = 2, 
                  position = position_dodge(dodge_width)) +
     geom_point(position = position_jitterdodge(dodge.width = dodge_width,
                                                jitter.width = jitter_width),
                alpha = 0.48) + 
-    scale_color_grey(labels = c('Females','Males')) + 
+    scale_color_manual(values = c('black', 'grey50'),
+                       labels = c('Females','Males')) + 
+    scale_shape_manual(values = c(17, 19), labels = c('Females', 'Males')) + 
     labs(x = 'Trap Color', y = 'Onion Maggot Fly Adults') +
     applied_entomology_theme 
 

### 2019-10-01 analysis/om_shape_trials_2005.R

@@ -85,13 +85,16 @@ jitter_width = 0.12
 set.seed(72)
 
 # generate figure
-shape_trial_figure <- ggplot(shape_trial[-31,], aes(x = treatment_shape, y = flies, color = sex)) + 
+shape_trial_figure <- ggplot(shape_trial[-31,], 
+                             aes(x = treatment_shape, y = flies, 
+                                 color = sex,
+                                 shape = sex)) + 
     stat_summary(fun.data = 'mean_cl_boot', 
                  geom = 'errorbar',
                  position = position_dodge(dodge_width),
-                 width = dodge_width/2) +
+                 width = dodge_width) +
     stat_summary(fun.data = 'mean_cl_boot',
-                 geom = 'point',
+                 geom = 'point', size = 2, 
                  position = position_dodge(dodge_width)) +
     geom_point(position = position_jitterdodge(dodge.width = dodge_width,
                                                jitter.width = jitter_width),
@@ -99,7 +102,9 @@ shape_trial_figure <- ggplot(shape_trial[-31,], aes(x = treatment_shape, y = fli
     geom_text(data = stat_labels, 
               aes(x = treatment_shape, y= 72, label = label),
               show.legend = FALSE) + 
-    scale_color_grey(labels = c('Females', 'Males')) + 
+    scale_color_manual(values = c('black', 'grey50'),
+                       labels = c('Females','Males')) + 
+    scale_shape_manual(values = c(17, 19), labels = c('Females', 'Males')) + 
     labs(x = 'Trap Shape', y = 'Onion Maggot Fly Adults') + 
     applied_entomology_theme
 

### 2019-10-01 analysis/om_size_trials.R

@@ -89,18 +89,23 @@ emmeans(size_mod_transform, ~ sex + size, type = 'response') %>%
 # generate contrasts
 size_means <- emmeans(size_mod_transform, ~ sex + size, type = 'response') %>%
     CLD(Letters = LETTERS, reversed = TRUE) %>% 
-    data.frame()
+    data.frame() %>%
+    mutate(.group = str_trim(.group))
 
 # Figure generation
-size_figure <- ggplot(size_means, aes(x = size, y = response, color = sex)) + 
-    geom_point(position = position_dodge(0.48)) + 
+size_figure <- ggplot(size_means, aes(x = size, y = response, 
+                                      color = sex, shape = sex)) + 
+    geom_point(position = position_dodge(0.48),
+               size = 2) + 
     geom_errorbar(aes(x = size, ymin = lower.CL, ymax = upper.CL),
                   position = position_dodge(0.48),
-                  width = 0.24) + 
-    geom_text(aes(x = size, y = upper.CL + 3, label = .group),
+                  width = 0.48) + 
+    geom_text(aes(x = size, y = upper.CL + 2, label = .group),
               position = position_dodge(0.48),
               show.legend = FALSE) + 
-    scale_color_grey(labels = c('Females', 'Males')) + 
+    scale_color_manual(values = c('black', 'grey50'),
+                       labels = c('Females','Males')) + 
+    scale_shape_manual(values = c(17, 19), labels = c('Females', 'Males')) + 
     labs(x = 'Trap Sphere Diameter (cm)', y = 'Onion Maggot Fly Adults') + 
     applied_entomology_theme
 

### 2019-10-01 manuscript/journal-applied-entomology/main.tex
added title page

@@
 \section*{Author Contribution}
-BAN, JPN, and SW designed the experiments.  DSW, CCF, and BAN analyzed the data and wrote the manuscript.
+BAN and JPN conceived and conducted the experiments. DSW and CCF performed statistical analysis.  DSW, CCF, and BAN wrote the manuscript.  All authors read and approved the manuscript.
 

### 2019-10-01 manuscript/journal-applied-entomology/title-page.tex
added title page

--- 2019-09-24 manuscript/journal-applied-entomology/main.tex
@@
 \begin{abstract}
-Onion maggot (\textit{Delia antiqua}) is an economically important pest of alliums in temperate regions throughout the world.
-Management of this pest is necessary to achieve economic returns and depends on insecticide regimes and cultural management.
-Both means of control rely upon effective monitoring of \textit{D.
-antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of adult onion maggot flies to accurately reflect population dynamics.
-We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult onion maggot flies in upstate New York.
-White, large diameter, spherical traps in conjunction with Delia Lure attractant performed the best in attracting and catching onion maggot adults.
-These results suggest an improved means of attracting and capturing onion maggot populations which could be useful in monitoring efforts and development of attract and kill strategies for pest control.
 
-% Please include a maximum of seven keywords
-\keywords{Onion Maggot, \textit{Delia antiqua}, attraction, sticky-trap, attract-and-kill, lure, onion management}
 \end{abstract}
 
-\linenumbers
-\section{Introduction}
-
-The onion maggot (\textit{Delia antiqua}) is an economically important pest of Allium crops worldwide.
-Found primarily in temperate climates, \textit{D.
-antiqua} is well established in onion growing regions in the Americas, Europe and Asia where crop losses due to this pest can range from 50 to 100 percent on onions (\textit{Allium cepa} L.), garlic (\textit{Allium sativem} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) if left unmanaged \citep{ellis1979factors,ning2017predicting,nault2007ecology, nault2006performance, nault2006onion}.
-Intensive management of this pest has become a necessary component of effective onion production in many parts of the world and severe damage from this pest continues to occur in areas where Allium crops are grown without rotation or where populations resistant to insecticides have developed \citep{martinson1988dispersal, nault2006onion}.
-
-Onion maggot is a primary pest in part due to its lifecycle.
-It is multivoltine with three generations per year in the Northern United States \citep{eckenrode1975population, hoepting2004insecticide}.
-Larvae feed on plant roots and allium bulbs causing the damage associated with this pest.
-First-generation infestations are particularly devastating as early feeding by onion maggot larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
-In addition, damaged plants become more susceptible to infestation by subsequent generations and pathogens \citep{eckenrode1986impact,nault2006performance}.
-Even if plants are not completely killed by onion maggot larvae, feeding damage often renders the produce unmarketable.
-
-Management of this pest has relied on prophylactic insecticide applications at planting \citep{nault2006performance}.
-A variety of organophosphate and carbamate insecticides have been used and discontinued \citep{nault2006performance}.
-Chlorpyrifos is commonly used as a drench treatment in combination with either cyromazine seed treatment (Trigard)  \citep{nault2006performance} or the seed treatment package containing thiamethoxam, spinosad and several fungicides (FarMore FI500).
-Cultural practices such as crop rotation, removal of damaged onions, and delayed planting are also effective management tactics \citep{martinson1988dispersal, finch1985influence, nault2011delaying}.
-
-In situations where an insecticide application at planting is not desired for onion maggot control, reliance on monitoring onion maggot adult activity in the field can be important for deploying curative management tactics.
-Additionally, effective monitoring becomes even more important where onion maggot is a relatively recent introduction or in areas where producers are not sure they have a problem.
-
-Past efforts at monitoring and understanding onion maggot phenology have relied on three principal methods: sticky traps, water traps, and simulation.
-Sticky traps and water traps have been used to varying degrees of success in North America and Europe but often suffer from limitations related to inefficiencies in counting \citep{thomingdeveloping,otto2000development}.
-Trap catch of adult onion maggot flies can be low compared to field populations.
-Additionally, the number of onion maggots caught compared to other insect collected in traps necessitates a great deal of time in evaluating trap catches.
-Odor sources of attractants also have been added to traps in an effort to make them more attractive, but with limited success.
-Simulation has relied on field data from traps, phenological studies in the lab, and climate information \citep{thomingdeveloping,otto2000development,ning2017predicting}.
-Population simulations can prove useful at larger scales, but often lack extremely detailed location specific information necessary for producers to determine if they have a severe problem in a specific field.
-
-To further develop effective monitoring methodologies for the onion maggot, we evaluated a number of factors likely to influence attraction of adult onion maggot flies.
-Previous work has suggested that color, shape, size, and chemistry all affect attraction of adult onion maggots \citep{harris1983color,harris1988host, thomingdeveloping, otto2000development}.
-We expanded on previous work in field trials over two years in upstate New York where a variety of novel trap designs with varying shape, size, color, and chemistry were presented to populations of adult onion maggot flies to evaluate ability to capture adult onion maggots.
-
-\section{Materials and Methods}
-
-To improve trap catch and monitoring of adult onion maggot fly, iterations of sticky traps of various shape, size, and color were evaluated in 2005 and 2006 in upstate New York.
-Additionally, after an improved shape, size, and color trap was developed, this trap was tested in conjunction with a Delia Lure (AgBio, Westminster, CO) attractant to evaluate potential improvement in trap catch.
-
-All shape, size, and color trials were conducted in commercial dry bulb onion fields on muck soil near Elba, NY in western upstate New York.
-Muck soils are high-organic matter soils formed from old lake beds.
-Trials evaluating trap catch in conjunction with Delia Lure were evaluated both in Elba, NY and on muck soil near Potter, NY in western upstate New York.
-All locations used in these studies are characterized by continuous onion production with no-rotation and consistently high onion maggot populations.
-No modifications were done to commercial weed, disease, or pest management and spray programs (which closely followed recommended management \citep{reiners2019}), the primary target of which is \textit{Thrips tabaci}.
-This management did not affect \textit{D.
-antiqua} populations as spray timing and efficacy of products targeting thrips have minimal to no impact on onion maggot fly \citep{finch1986behavior}.
-
-\subsection{Field Trials}
-
-For all field trials, numbers of male and female \textit{D. antiqua} flies were recorded weekly from traps beginning in late May and ending in late June.
-
-\paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult onion maggot fly, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with Tanglefoot sticky material (The Scotts Company LLC, Maryville, OH) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
-Traps were spaced 15.2 meters apart and arranged in a randomized control block design with five replications.
-
-\paragraph{Size Trial}
-To evaluate the influence of trap size on trap catch and monitoring of adult onion maggot fly, white spherical sticky traps with diameters of 5.00, 6.25, 7.50, 8.75, and 10.00 cm were placed along the long edge of onion fields with spacing 15.2 meters apart in a randomized controlled block design with five replications.
-
-\paragraph{Color Trial}
-To evaluate the effect of color on trap catch and monitoring of adult onion maggot fly, white, yellow, green, and red spherical sticky traps 8.75 cm in diameter were placed along the long edge of onion fields in a randomized controlled block design with five replications.
-
-\paragraph{Delia Lure Trial}
-To evaluate the effect of adding a chemical attractant to enhance trap catch and monitoring of adult onion maggot flies, white spherical sticky traps 8.75 cm in diameter were placed at the edge of onion fields in a paired design where half of the traps received a Delia Lure (Baited) and the other half did not (Unbaited).
-Trap catch was monitored three times throughout the season and four replications of each treatment were conducted in each location.
-
-\subsection{Analysis}
-
-Raw data from shape, size, and color trials were analyzed using linear models and analysis of variance.
-Models were determined after consideration of all factor combinations and interactions and selected based on consideration of residual diagnostics (conformance to assumptions of normality and homoscedasticity), goodness of fit tests, $R^2$ values, information criteria, and leverage considerations.
-Based on these considerations, an outlier was detected and removed from the shape trials (P = 0.032, Bonferroni Outlier Test) and data from the size and color trials were square root transformed to conform with assumptions of normality and homoscedasticity.
-
-Raw data from the Delia Lure Trial were analyzed with a paired t-test due to the nature of the experimental design.
-Conformation to assumptions of normality were confirmed through examination of quantile-quantile plots.
-
-\subsection{Data Management}
-
-All data for the trials were entered into flat tabular (.csv) files.
-All analysis on the raw data was conducted in R version 3.5.2 using RStudio as an IDE (with Vim keybindings) \citep{rcore2018,rstudio}.
-The $tidyverse$, $car$, and $emmeans$ packages were used to facilitate analysis \citep{tidy, car, emmeans}.
-All code, including manuscript documentation, is available on GitHub (https://github.com/acetworld/onion-maggot-attraction).
-
-\section{Results}
-
-\paragraph{Shape Trial} Models relating trap shape and \textit{D.
-antiqua} sex to trap catch significantly explained approximately 70\% of observed variation (P \textless 0.001, $R^2_{adj}$ = 0.70, Table \ref{table:1}).
-Trap shape significantly influenced (P = 0.005) catch of adult \textit{D.
-antiqua} (Figure \ref{fig:figure1}).
-Sticky traps caught approximately 27.8 $\pm$ 2.8 more females than males.
-Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.
-While there were no significant differences between numbers of females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.
-No significant differences were observed among treatments for male trap catch.
-
-\begin{table}[]
-\caption{Linear model and analysis of variance results and diagnostics for shape, size, and color trials.
-Treatment refers to the factor under evaluation.
-For the shape trial, treatment denotes shape; for the size trial, treatment denotes size; for the color trial, treatment denotes color.
-Missing values indicate that factor was not included in the best fit model.
-All code and additional documentation is available on GitHub.
-}
-\begin{tabular}{lrrrrrrrrr}
-              & \multicolumn{9}{c}{Trial}                                                                                                                                                                                                \\ \cline{2-10}
-              & \multicolumn{3}{c}{Shape}                                              & \multicolumn{3}{c}{Size}                                               & \multicolumn{3}{c}{Color}                                              \\
-              & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{F} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{P} \\ \cline{2-10}
-Sex           & 42                    & 1                      & \textless 0.0001      & 197.5                 & 1                      & \textless 0.0001      & 37.2                  & 1                      & \textless 0.0001      \\
-Treatment     & 4.4                   & 4                      & 0.005                 & 11.6                  & 4                      & \textless 0.0001      & 31.3                  & 3                      & \textless 0.0001      \\
-Year          &                       &                        &                       & 142.4                 & 1                      & \textless 0.0001      &                       &                        &                       \\
-Sex:Treatment &                       &                        &                       &                       &                        &                       & 6.3                   & 3                      & 0.002                 \\
-Sex:Year      &                       &                        &                       & 137.9                 & 1                      & \textless 0.0001      &                       &                        &                       \\ \cline{2-10}
-              &                       &                        &                       &                       &                        &                       &                       &                        &                       \\
-$R^2$            &                       &                        & 0.75                  &                       &                        & 0.75                  &                       &                        & 0.83                  \\
-$R^2_{adj}$         &                       &                        & 0.70                  &                       &                        & 0.73                  &                       &                        & 0.79                  \\
-P             &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001      &                       &                        & \textless 0.0001
-\end{tabular}
-\label{table:1}
-\end{table}
-
-\paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.73, Table \ref{table:1}).
-Numbers of females captured were significantly greater than numbers of males, especially in 2005.
-Trap size significantly influenced trap catch (P \textless 0.001).
-Increasing diameter of trap size showed a trend towards increasing trap catch (Figure \ref{fig:figure2}) with the largest trap catching significantly more females and males.
-While male trap catch was less than that of females, trends in catch among the different diameters were similar for both males and females.
-
-\paragraph{Color Trial} Models using color and sex to explain observed trap catch significantly explained approximately 79\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.79, Table \ref{table:1}).
-Color significantly influenced trap catch (P \textless 0.001) with white traps catching significantly more females than any other color (t \textless -3.1, df = 32, P \textless 0.012) and significantly more males than any other color except yellow (t \textless -3.1, df = 32, P \textless 0.012, Yellow: t = -1.6, df = 32, P = 0.3).
-White traps caught significantly more females than males (t = 6.1, df = 32, P \textless 0.001).
-
-\paragraph{Delia Lure Trial} The presence of Delia Lure in conjunction with sticky traps increased catch of adult onion maggot flies.
-Traps baited with Delia Lure caught approximately 51.3 (95\% CI: 7.3-95.4) more adults than traps without the Delia Lure bait (t = 3.0, df = 5, P = 0.03).
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-1.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on sticky traps of different shape.
-Shaded points denote raw values while solid points and error bars denote mean and bootstrapped 95\% confidence intervals respectively.
-Letters not shared between groups denote significant differences in female trap catch (there was no observed difference in male trap catch) at $\alpha$ = 0.05 with Tukey's HSD test.
-}
-\label{fig:figure1}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-2.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on spherical sticky traps of different size.
-Points and error bars denote mean and 95\% confidence intervals respectively.
-Letters not shared between groups indicates significant differences in adult catch at $\alpha$ = 0.05 with Tukey's HSD test.}
-\label{fig:figure2}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-3.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on spherical sticky traps of different color.
-Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
-\textbf{*} indicates significantly different trap catch on white sticky traps (P = 0.012).}
-\label{fig:figure3}
-\end{figure}
-
-\begin{figure}[bt]
-\centering
-\includegraphics[width = 8cm]{figures/publication/figure-4.pdf}
-\caption{Adult onion maggot fly catch per trap over the sampling period on sticky traps baited with Delia Lure attractant and unbaited.
-Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
-\textbf{*} indicates significantly different trap catch on baited and unbaited traps (P = 0.030).
-}
-\label{fig:figure4}
-\end{figure}
-
-\section{Discussion}
-
-Varying the shape, size and color of sticky traps revealed that changes in these factors can increase catch of adult onion maggot flies.
-Short cylinder traps performed better than most other shapes and were not significantly different from spherical traps.
-Spherical traps were more economical to produce and use so they were selected for use in subsequent studies.
-Size played a large role in increasing trap catch.
-Larger diameter traps with more surface area captured more adult onion maggot flies.
-Color had perhaps the largest impact on catch of adult onion maggot flies with white traps far outperforming yellow, green and red traps.
-
-The combination of sticky traps with the chemical attractant, Delia Lure, also increased catch of adult onion maggot flies suggesting that onion maggot adults use a combination of visual and olfactory cues as suggested in previous studies \citep{harris1983color, harris1988host}.
-Our work suggests that all of these factors play a role in onion maggot attraction in the field and expands upon previous work in the laboratory suggesting that no one factor is critical in onion maggot attraction \citep{harris1988host}.
-
-Sticky traps were chosen for this study in lieu of water traps because of their ease of use (replacing water is not necessary, and rain is not a problem) and because previous work has shown them to be more effective that water pan traps at catching onion maggot adults \citep{thomingdeveloping}.
-This work showed that white traps far outperform sticky traps of other colors confirming findings in another study that white traps work well for \textit{Delia} flies.
-Interestingly, other work has suggested that specificity for \textit{D.
-antiqua} could be improved with the color blue, but that overall trap catch may suffer \citep{thomingdeveloping}.
-
-These results suggest a way forward in improving trapping of onion maggot fly adults in the field.
-A spherical, white, large diameter sticky trap baited with Delia Lure is the best option for monitoring adult onion maggot flies based on the various factors tested in these trials.
-Improved trapping ability of white large diameter traps may improve monitoring efforts in situations where it is desirable to understand onion maggot phenology, develop decision support tools, measure range, and understand inter- and intra-generational spatio-temporal dynamics.
-This improved trapping could then inform modeling efforts and predictive management abilities \citep{ning2017predicting, otto2000development,thomingdeveloping}.
-
-Sticky traps have been used in monitoring and control efforts of other visually responsive flies.
-Orange spheres have been effective at attracting and trapping Caribbean Fruit Fly (\textit{Anastrepha suspensa} Lowe) \citep{sivinski1990colored}.
-Apple maggot (\textit{Rhagoletis pomonella} Walsh) management, in particular, has benefited from development of red spherical traps for monitoring field populations \citep{prokopy1975apple, drummond1984comparative, duan1994apple}.
-This work has even expanded into control methods with trapping using these spheres reducing pest populations and used in conjunction with other strategies \citep{bostanian1999managing}.
-
-The ability to attract larger numbers of adult onion maggot flies also creates an opportunity for a different, more environmentally friendly, management method.
-If larger numbers of flies can be attracted and then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of onion maggot could be reduced.
-'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.
-Using large, white, spherical traps in conjunction with Delia Lure may provide the attraction needed to make it possible to control these pests using attract and kill strategies.
-
-\section*{Acknowledgements}
-We appreciate technical assistance by M.
-Hessney and Delia Lure from J.
-Meneley.
-Starker Wright aided in development and construction of traps.
-The New York State Integrated Pest Management Program, USDA/CSREES Pest Management Alternatives Program, and New York State Department of Agriculture and Markets Onion Research and Development Program supported this research.
-
-\section*{Conflict of Interest}
-The authors declare no conflict of interest.
-
-\section*{Author Contribution}
-BAN, JPN, and SW designed the experiments.  DSW, CCF, and BAN analyzed the data and wrote the manuscript.
-
-\section*{Data Availability Statement}
-All code and data, including manuscript documentation, is available on GitHub(https://github.com/acetworld/onion-maggot-attraction).
-
-%\printendnotes
-
-% Submissions are not required to reflect the precise reference formatting of the journal (use of italics, bold etc.), however it is important that all key elements of each reference are included.
-
-\section{References}
-
-\bibliographystyle{vancouver-authoryear}
-\bibliography{om-attraction}
-
-%\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}
-
 \end{document}

### 2019-12-27 manuscript/journal-applied-entomology/reviewer-response/reviewer-response.tex
reviewer responses

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{changepage}% http://ctan.org/pkg/changepage
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{scrextend}
\usepackage{lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{\includegraphics[height= 1cm]{ento1.png}\vspace{1em}}
\chead{\includegraphics[width = 5cm]{agritech1.png}}
\lhead{\includegraphics[width=3cm]{acet1.png}}

\fancyfoot{}
\setlength\headheight{40.8pt}
\RequirePackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\fontsize{10}{15}\bfseries}{\thesection}{0em}{}
\titlespacing{\section}{}{1.24em}{0.24em}

\cfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\begin{document}

\begin{addmargin}[2.8in]{}
Willett, Filgueiras, \newline
Nyrop and Nault \newline
----------------------------- \newline
Denis S. Willett\newline
Department of Entomology \newline
Cornell AgriTech  \newline
Cornell University \newline
15 Castle Creek Drive \newline
Geneva, NY 14456 \newline
deniswillett@cornell.edu \newline
\end{addmargin}
\setlength{\parindent}{0cm}

December 24, 2019

\vspace{1.24em}

Journal of Applied Entomology

\vspace{1.24em}

Dear Prof. Stefan Vidal,

\vspace{0.48em}
\setlength{\parindent}{1.24cm}

Thank you for your consideration of \textit{“Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping”} for publication in the Journal of Applied Entomology.  We have revised the manuscript in accordance with reviewer recommendations.  A complete and detailed account of the revisions is included below.  The reviewer comments were very helpful, much appreciated, and have resulted in a better manuscript.  In addition to submitting a revised version of the manuscript incorporating the latest changes, we are also submitting production quality images.

\vspace{2em}

Much appreciated, \newline

\vspace{1em}

Denis S. Willett
\vspace{0.48em}

Camila C. Filgueiras
\vspace{0.48em}

Jan P. Nyrop
\vspace{0.48em}

Brian A. Nault
\vspace{0.48em}

\vspace{1.4em}

\hline

\setlength\parindent{0pt}

\subsection*{Reviewer 1 (Remarks to the Author)}

You spend a lot of time talking about relative tolerance of the bermudagrass lines to sting nematode. However, I was never very clear on how you are defining tolerance or how this was determined.

\begin{quote}
    \textit{This is an excellent question.  We have taken the opportunity to elaborate on this in the introduction.  In short, tolerance in bermudagrass is determined if there was no reduction in root length or had greater root length than ‘Tifway’ despite \textit{B. longicaudatus} infection.  Tolerance of the varieties had been established in previous work by Pang et al. 2011, citations 23, and 24 in the manuscript.  } 
\end{quote}

On page 2 under Bermudagrass response to sting nematode feeding...I think you should use the term nematode population densities instead of "nematode densities" or "differences in nematode population."

\begin{quote}
    \textit{Thanks for pointing this out.  We have adjusted the language in that section in accordance with your suggestions.} 
\end{quote}

Very well written and very interesting paper

\begin{quote}
    \textit{Thank you for your interest and constructive feedback.}
\end{quote}

\subsection*{Reviewer #2 (Technical Comments to the Author)}

This is a well researched study and the manuscript well structured and written. The methods used are scientifically sound, results appropriately interpreted and discussed. Except for a few minor comments below, I recommend publication of this manuscript.

\begin{quote}
    \textit{Thank you for your feedback.  We appreciate the interest and comments below.}
\end{quote}

Line 58. The authors stated that the canonical correspondence analysis explained 42\% of the observed inertia in the total metabolome. I suggest that the authors explain this because in Figure 2 this analysis explained 71.9\% of the total metabolome variation (CCA1: 45.3\% + CCA2: 26.6\%).

\begin{quote}
  \textit{Thanks for your inquiry.  Canonical correspondence analysis did explain 42\% of the observed inertia.  Of that 42\% explained inertia, axis 1 explained 45.3\% and axis 2 26.6\%.  Summing the explained variation of the other 3 axis with the first two would result in 100\% of the variation captured in canonical ordination or 42\% of observed inertia (constrained $\chi^2$) in the total metabolome. This explanation has been elaborated upon in the text.   } 
\end{quote}

Lines 146 and 150. Change ‘conetainers’ to ‘containers and container’

\begin{quote}
    \textit{Thanks for suggesting this. Conetainers should be Cone-tainers to refer to the specific type of container used to house the plants.  We have clarified this in the Methods section adding both information about the company from which they can be procured and changing the spelling in lines 148 and 150 for clarification.  }
\end{quote}

I suggest that instead of putting in the appendix, the package names used for their statistical analysis, the authors should include these names in the text to educate readers, especially for those not familiar with the ‘R software’

\begin{quote}
    \textit{Thanks for your suggestion.  This is a good idea; we have incorporated names of the software packages in the main body of the text.}
\end{quote}

\end{document}

### 2019-12-27 manuscript/journal-applied-entomology/title-page.tex
reviewer responses

@@
 
+\section*{Acknowledgements}
+We appreciate technical assistance by M.
+Hessney and Delia Lure from J.
+Meneley.
+Starker Wright aided in the development and construction of traps as well as experimental design.
+The New York State Integrated Pest Management Program, USDA/CSREES Pest Management Alternatives Program, and New York State Department of Agriculture and Markets Onion Research and Development Program supported this research.
+
 \end{document}

### 2020-01-02 manuscript/journal-applied-entomology/main.tex
updated reviewer response

@@
 Management of this pest is necessary to achieve economic returns and depends on insecticide regimes and cultural management.
-Future management strategies for \textit{D.
-antiqua} may rely upon effective monitoring of \textit{D.
-antiqua} populations, but traditional means of monitoring can be ineffective at catching sufficient numbers of \textit{D.
-antiqua} flies to accurately reflect population dynamics.
+Current cultural management especially altering planting date, field location, and crop rotation depend on monitoring.
 We evaluated the effect of shape, size, color and chemical attractants on trap catch of field populations of adult \textit{D.
@@
 antiqua} larvae can kill seedlings \citep{nault2006onion, nault2006performance}.
-In addition, damaged plants become more susceptible to infestation by subsequent generations and pathogens \citep{eckenrode1986impact,nault2006performance}.
+In addition, damaged plants become more susceptible to infestation by subsequent generations and plant pathogens \citep{eckenrode1986impact,nault2006performance}.
 Even if plants are not completely killed by \textit{D.
@@
 In situations where an insecticide application at planting is not desired for \textit{D.
-antiqua} control, reliance on monitoring \textit{D.
+antiqua} control (such as organic management systems), reliance on monitoring \textit{D.
 antiqua} adult activity in the field can be important for deploying curative management tactics.
@@
 \paragraph{Shape Trial} To evaluate effect of trap shape on trap catch and monitoring of adult \textit{D.
-antiqua} flies, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with Tanglefoot sticky material (The Scotts Company LLC, Maryville, OH) and placed along the long edge of an onion (\textit{Allium cepa} L.) field near Elba, NY.
+antiqua} flies, square, cube, short cylindrical, tall cylindrical, and spherical semi-gloss white shapes each with a surface area of 180 $cm^2$  were coated with Tanglefoot sticky material (The Scotts Company LLC, Maryville, OH) and placed along the long edge of rectangular onion (\textit{Allium cepa} L.) fields near Elba, NY.
 Traps were spaced 15.2 meters apart and arranged in a randomized control block design with five replications.
@@
 \paragraph{Shape Trial} Models relating trap shape and \textit{D.
-antiqua} sex to trap catch significantly explained approximately 70\% of observed variation (P \textless 0.001, $R^2_{adj}$ = 0.70, Table \ref{table:1}).
+antiqua} sex to trap catch significantly explained approximately 70\% of observed variation (Table \ref{table:1}).
 Trap shape significantly influenced (P = 0.005) catch of adult \textit{D.
@@
 Short cylindrical traps outperformed square panel and tall cylinder traps in terms of female trap catch.
-While there were no significant differences between numbers of females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres.
+While there were no significant differences between numbers of females captured on short cylinder, sphere, and cube traps, short cylinders tended to outperform cubes and spheres catching 10.4$\pm$ 6.2 (P = 0.3) more females.
 No significant differences were observed among treatments for male trap catch.
@@
 
-\paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.73, Table \ref{table:1}).
+\paragraph{Size Trial} Models using size, sex, and year to explain observed trap catch significantly explained approximately 73\% of the observed variation (Table \ref{table:1}).
 Numbers of females captured were significantly greater than numbers of males, especially in 2005.
@@
 
-\paragraph{Color Trial} Models using color and sex to explain observed trap catch significantly explained approximately 79\% of the observed variation (P \textless 0.001, $R^2_{adj}$ = 0.79, Table \ref{table:1}).
+\paragraph{Color Trial} Models using color and sex to explain observed trap catch significantly explained approximately 79\% of the observed variation (Table \ref{table:1}).
 Color significantly influenced trap catch (P \textless 0.001) with white traps catching significantly more females than any other color (t \textless -3.1, df = 32, P \textless 0.012) and significantly more males than any other color except yellow (t \textless -3.1, df = 32, P \textless 0.012, Yellow: t = -1.6, df = 32, P = 0.3).
@@
 antiqua} fly catch per trap over the sampling period on sticky traps baited with Delia Lure attractant and unbaited.
-Shaded points denote raw values while solid points and error bars denote means and bootstrapped 95\% confidence intervals respectively.
+Shaded points denote total replicate values while solid points and error bars denote global means and bootstrapped 95\% confidence intervals respectively.
 \textbf{*} indicates significantly different trap catch on baited and unbaited traps (P = 0.030).
@@
 antiqua} flies with white traps far outperforming yellow, green and red traps.
+Interestingly, catch of male flies was consistently lower than catch of female flies suggesting differences in dispersion or attraction to tested designs.
 
@@
 Sticky traps have been used in monitoring and control efforts of other visually responsive flies.
+Carrot rust fly (\textit{Psila rosae}) and cabbage fly (\textit{Delia radicum}) have been monitored and managed using trapping data for over a decade \citep{stevenson1981carrot,collier1990monitoring,getzin1983carrot, broatch1997comparison, finch1990effectiveness}.
 Orange spheres have been effective at attracting and trapping Caribbean Fruit Fly (\textit{Anastrepha suspensa} Lowe) \citep{sivinski1990colored}.
 Apple maggot (\textit{Rhagoletis pomonella} Walsh) management, in particular, has benefited from development of red spherical traps for monitoring field populations \citep{prokopy1975apple, drummond1984comparative, duan1994apple}.
-This work has even expanded into a control method by trapping apple maggot flies using these spheres in conjunction with other strategies, which hasreduced infestations \citep{bostanian1999managing}.
+This work has even expanded into a control method by trapping apple maggot flies using these spheres in conjunction with other strategies, which has reduced infestations \citep{bostanian1999managing}.
 
 The ability to attract larger numbers of adult \textit{D.
-antiqua} flies also creates an opportunity for a different, more environmentally friendly, management method.
-If larger numbers of flies can be attracted and then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of \textit{D.
-antiqua} could be reduced.
-'Attract and kill' and 'Lure and kill' methodologies have been applied in pest management systems to moths, weevils, and other flies \citep{el2009potential,el2011bait,navarro2013efficacy,charmillot2000attract}.
-Using large, white, spherical traps in conjunction with Delia Lure may provide the attraction needed to make it possible to control these pests using attract and kill strategies.
+antiqua} flies also creates an opportunity for improving current management methods in an integrated pest management context.
+Current cultural management especially altering planting date, field location, and crop rotation depend on monitoring.
+While trap catch alone is not a measure of monitoring efficacy, the higher numbers of \textit{D.
+antiqua} flies caught in these traps could potentially be used to develop better monitoring approaches.
+If larger numbers of flies can be attracted to these traps, and then killed either by adhering to a sticky substance or coming into contact with an insecticide, populations of \textit{D.
+antiqua} may be able to be reduced.
 

### 2020-01-02 analysis/om_shape_trials_2005.R
updated analysis with reviewer feedback

@@ -67,7 +67,10 @@ model_diagnostics(shape_mod_xoutlier, to_plot = FALSE)
 emmeans(shape_mod_xoutlier, ~sex ) %>% contrast(method = 'tukey')
 
 emmeans(shape_mod_xoutlier, ~sex*treatment_shape) %>% 
-    cld(by = 'sex')
+    CLD(by = 'sex')
+
+emmeans(shape_mod_xoutlier, ~ sex * treatment_shape) %>% 
+    contrast(by = 'sex', method = 'trt.vs.ctrl')
 
 stat_labels <- emmeans(shape_mod_xoutlier, ~sex*treatment_shape) %>% 
     cld(by = 'sex') %>% data.frame() %>% 
